---
title: 'TITLE X'
subtitle: 'Supplemental materials for submittal to X'
author: 
  - Paula Williams
  - J. Leah Jones-Crank
  - Bassel Daher
  - Alyssa Thomas
  - Erich Seamon
  - Ruchie Pathak
  - Dan Cronan
  - Meghna Babbar-Sebens
  - Andrew Kliskey
date: "`r Sys.Date()`"
always_allow_html: yes
output:
  pdf_document:
    toc: yes
  includes:
      in_header: header.tex
params: null
mainfont: serif
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

# Supplemental Materials Summary

This analysis focuses on examining if how stakeholder engagement, and the level of engagement, impacts whether a solution for research outcomes is proposed and/or implemented.  This meta-synthesis of 483 papers were evaluated and coded using several differing engagement scales. Additionally, each paper was coded by the geographic scale, and whether a computational model was used as part of the research. 



```{r echo=FALSE, warning=FALSE, message=FALSE}

library(ggplot2)
library(epiDisplay)
library(caret)

crcdata <- read.csv("./data/crc_data_ES2.csv")
crcdata_new <- read.csv("./data/crc_data_aug25.csv")

#set YN to 01
require(dplyr)
crcdata <- crcdata %>%
  mutate(solution_proposed_YN = ifelse(solution_proposed_YN == "N",0,1))

require(dplyr)
crcdata <- crcdata %>%
  mutate(solution_implemented_YN = ifelse(solution_implemented_YN == "N",0,1))

require(dplyr)
crcdata <- crcdata %>%
  mutate(S_stakeholder_engagment_YN = ifelse(S_stakeholder_engagment_YN == "N",0,1))

#fix colnames
names(crcdata)[names(crcdata) == 'STE_IAP2_NA'] <- 'STE_IAP2_data_gathering'
names(crcdata)[names(crcdata) == 'G_na'] <- 'G_nogeography'

names(crcdata)[43] <- "SC_researcher"

names(crcdata)[51] <- "G_notdescribed"


```


\newpage

# Variable Summary

Below is a list of the categorical variables generated from the literature reviews

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
df <- data.frame(Variables = c("Year", "Solution Proposed", "Solution Implemented", "Solution Type", "Computational Model Used", "Researcher Type", "Stakeholder Type", "Stakeholder Engagment Scale - Ghodsvali", "Stakeholder Engagment Scale - IAP2", "Stakeholder Engagement Scale - Local", "Geographical Type"), Description = linebreak(c("Year of citation", "Was a solution proposed?", "Was a solution implemented?","If a solution was proposed, what was the solution type? Groups include: Technology, Policy, Institutional, Social, Economic, Ecological, and Educational.", "Was a computational model used?", "What was the research type?  Groups include: NGO, English, Math, Computer Science, Physics, Engineering, Interdisciplinary, Social Science, Economics, Agriculture, and Other","What was the stakeholder type? Groups include: Farmers, Combined Government, Combined Coalition, Combined Industry, Migrants, Youth, Public, Univerity, and Experts", "If a stakeholder was engaged, categorization of the engagement using the Ghodsvali scale. Groups include: Nominal, Instrumental, Representation, and Transformative", "If a stakeholder was engaged, categorization of the engagement using the IAP2 scale. Groups include: Data Gathering, Inform, Consult, Involve, Collaborate, and Empower", "If a stakeholder was engaged, categorization of the engagement using a customized scale. Groups include: Researcher, Data Gathering, Inform, Perspectives, Planning, Identify, Envision, and Implement", "What the geography type? Groups include: Not Described, Local, Regional, National, Multinational, Global, and No Geography")))
kable(df, col.names = c("Variable Name", "Description"), escape = F, caption = "Table T1: Variable Descriptions") %>% column_spec(2, width = "2in") %>% column_spec(c(1:2), width = "2.5in") %>% kable_styling(full_width = FALSE,latex_options = c("hold_position", "scale_down"), font_size = 8) %>% collapse_rows(columns = 2) %>% kable_classic_2(full_width = F) %>% row_spec(0,bold=TRUE)

```


<!-- \newpage -->

<!-- # Variable Summary REFINED -->

<!-- Below is a list of the categorical variables generated from the literature reviews REFINED -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->
<!-- library(knitr) -->
<!-- library(kableExtra) -->
<!-- df <- data.frame(Variables = c("Year", "Solution Proposed", "Solution Implemented",  "Stakeholder Type", "Stakeholder Engagment Scale - Ghodsvali", "Stakeholder Engagment Scale - IAP2", "Stakeholder Engagement Scale - Local"), Description = linebreak(c("Year of citation", "Was a solution proposed?", "Was a solution implemented?","What was the stakeholder type? Groups include: Farmers, Combined Government, Combined Coalition, Combined Industry, Migrants, Youth, Public, Univerity, and Experts", "If a stakeholder was engaged, categorization of the engagement using the Ghodsvali scale. Groups include: Nominal, Instrumental, Representation, and Transformative", "If a stakeholder was engaged, categorization of the engagement using the IAP2 scale. Groups include: Data Gathering, Inform, Consult, Involve, Collaborate, and Empower", "If a stakeholder was engaged, categorization of the engagement using a customized scale. Groups include: Researcher, Data Gathering, Inform, Perspectives, Planning, Identify, Envision, and Implement"))) -->
<!-- kable(df, col.names = c("Variable Name", "Description"), escape = F, caption = "Table T1: Variable Descriptions") %>% column_spec(2, width = "2in") %>% column_spec(c(1:2), width = "2.5in") %>% kable_styling(full_width = FALSE,latex_options = c("hold_position", "scale_down"), font_size = 8) %>% collapse_rows(columns = 2) %>% kable_classic_2(full_width = F) %>% row_spec(0,bold=TRUE)  -->

<!-- ``` -->


\newpage

# Chi-Square Testing
## Chi Square Testing: solution proposed or not vs. vs. stakeholder engagement

Chi Square and Fishers Exact Test on contingency table with Solution/No Solution as the explanatory variable, and engaged stakeholder/did not engage stakeholder as the response variable. 

**ChiSquare = 26: Fishers Exact Test Odds Ratio: 10: Not Independent**

Both chi square and fishers exact test were significant, with a chi square approximation of ~26, which is well above the critical value (3.84 with one degree of freedom).  Fishers Exact Test returned an odds ratio of ~10. The alternative hypothesis: true odds ratio is not equal to 1, therefore the null hypothesis is rejected - the groups are not independent. 

The Fishers Exact Test defaults to associating the odds ratio (which can represent effect size) with the first cell. In this instance "The odds of having a solution is 10 times that for an engaged stakeholder".  You could flip the response and explanatory variables, but the odds ratio would stay the same.

For more info on this topic see: Kim HY. Statistical notes for clinical researchers: Chi-squared test and Fisher's exact test. Restor Dent Endod. 2017 May;42(2):152-155. doi: 10.5395/rde.2017.42.2.152. Epub 2017 Mar 30. PMID: 28503482; PMCID: PMC5426219.


```{r, echo=FALSE}
library(Barnard)

crcdata$solution_proposed_YN <- as.factor(crcdata$solution_proposed_YN)
crcdata$S_stakeholder_engagment_YN <- as.factor(crcdata$S_stakeholder_engagment_YN)
crcdata$solution_implemented_YN <- as.factor(crcdata$solution_implemented_YN)

levels(crcdata$S_stakeholder_engagment_YN) = c("N", "Y")
levels(crcdata$S_stakeholder_engagment_YN) = c("N", "Y")
levels(crcdata$solution_proposed_YN) = c("N", "Y")
levels(crcdata$solution_implemented_YN) = c("N", "Y")

crcdata_table <- table(crcdata$solution_proposed_YN, crcdata$S_model_YN)
colnames(crcdata_table) <- c("M", "NM")

#custom add
crcdata_table <- rbind(crcdata_table[2,], crcdata_table[1,])
crcdata_table[1,] <- rev(crcdata_table[1,])

solution_stakeholder <- crcdata_table

 # solution_stakeholder <- 
 #   as.matrix(
 #     read.table(text=
 #                  "  E     NE           
 #       S             14    4      
 #       NS            76    400",
 #                header=TRUE,
 #                row.names=1)
 #   )

names(dimnames(solution_stakeholder)) <- c('solution','stakeholder')
solution_stakeholder

solution_stakeholder <- as.table(solution_stakeholder)

summary(solution_stakeholder)

fisher.test(solution_stakeholder)

btest <- c(solution_stakeholder[1,1:2], solution_stakeholder[2,1:2])

barnard.test(13,5,95,370)

```

\newpage

## Chi Square Testing: solution proposed or not vs. computational model used or not? 

Chi Square and Fishers Exact Test on the contingency table with solution proposed (solution/no solution) as the explanatory variable, and whether a computational model used (model/no model) as the response variable.

**ChiSquare = .57: Fishers Exact Test Odds Ratio = .668: Independent**

Both chi square and fishers exact test (FET) were insignificant/borderline, with a chi square approximation of ~.57, which is well below to the critical value (3.84 for one degree of freedom).  FET returned an odds ratio of under 1, therefore the null is accepted - the groups are independent.

The FET defaults to associating the odds ratio (which can represent effect size) with the first cell. In this instance "The odds of having a solution is .67 times that for having a model".  You could flip the response and explanatory variables, but the odds ratio would stay the same.

```{r, echo=FALSE}
library(Barnard)

crcdata$S_model_YN <- as.factor(crcdata$S_model_YN)

crcdata$S_model_YN <- factor(crcdata$S_model_YN, levels = c("Y", "N"))

crcdata_table <- table(crcdata$solution_proposed_YN, crcdata$S_model_YN)
colnames(crcdata_table) <- c("M", "NM")

crcdata_table <- rbind(crcdata_table[2,], crcdata_table[1,])
#crcdata_table[2,] <- rev(crcdata_table[2,])


solution_model <- 
 crcdata_table

 
 # solution_model <- 
 #   as.matrix(
 #     read.table(text=
 #                  "  M     NM      
 #       S             11    7      
 #       NS            377   94",
 #                header=TRUE,
 #                row.names=1)
 #   )

names(dimnames(solution_model)) <- c('solution','model')
solution_model

solution_model <- as.table(solution_model)

summary(solution_model)

fisher.test(solution_model)

barnard.test(13,5,370,95)
```

\newpage

# Summary Statistics Graphs

## Were solutions proposed in the set of all papers?

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(crcdata,aes(x=solution_proposed_YN, fill=year)) + ggtitle("Solution Proposed: Y=18") + labs(x="Was a solution proposed?") +
  geom_bar(stat = "count", position = "dodge", fill="#99CC99") + theme_minimal() + theme_minimal()+
  theme(text = element_text(),
        axis.text.x = element_text(angle = 0, hjust = 1)) 

```
\newpage

## Were solutions implemented in the set of all papers?

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(crcdata,aes(x=solution_implemented_YN, fill=year)) + ggtitle("Solution Implemented: Y=11") + labs(x="Was a solution implemented?") + geom_bar(stat = "count", position = "dodge", fill="#99CC99") + theme_minimal()+
  theme(text = element_text(),
        axis.text.x = element_text(angle = 0, hjust = 1)) 

```
\newpage

## What were the solution types?

```{r echo=FALSE, warning=FALSE, message=FALSE}

# par(mar = c(8,4,4,4))
# plot3 <- barplot(colSums(crcdata[,4:10]), las=2, main="Solution Types: N=18", names.arg = c("Technological", "Policy", "Institutional", "Social", "Economic", "Ecological", "Educational"))

plot3_data <- colSums(crcdata[,4:10])
p3a <- as.data.frame(plot3_data)
p3a$group <- c("Technological", "Policy", "Institutional", "Social", "Economic", "Ecological", "Educational")

# 
ggplot(p3a, aes(x=group, y=plot3_data)) + geom_bar(stat="identity",fill="#99CC99") + theme_bw() + theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
  xlab("Solution Types") + ylab("Count")


```
\newpage

## Was a computational model used?

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(crcdata,aes(x=S_model_YN, fill=year)) + ggtitle("Computational Model Used: Y=366") + labs(x="Was a computational model used?") +
  geom_bar(stat = "count", position = "dodge", fill="#99CC99") + theme_minimal()
 
``` 
\newpage

## Were stakeholders engaged?

```{r echo=FALSE, warning=FALSE, message=FALSE}

# nrow(subset(crcdata, solution_proposed_YN == "1"))/nrow(subset(crcdata, solution_proposed_YN == "0"))
# 
# nrow(subset(crcdata, solution_implemented_YN == "1"))/nrow(subset(crcdata, solution_implemented_YN == "0"))


#stakeholder
#par(mar = c(4,4,4,4))
#barplot(table(crcdata$S_stakeholder_engagment_YN), main = "Stakeholder Engagment: Y=92")

ggplot(crcdata,aes(x=S_stakeholder_engagment_YN, fill=year)) + ggtitle("Stakeholder Engagement: YES=92") + labs(x="Were stakeholders engaged?") +
  geom_bar(stat = "count", position = "dodge", fill="#99CC99") + theme_minimal()

```
\newpage

## All FEWS papers by year

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
crcdata_remove2011 <- subset(crcdata, year != "2011")
ggplot(crcdata_remove2011, aes(x=year)) + 
    geom_bar(stat="count")+theme_bw() + scale_x_continuous(breaks = crcdata$year) +
  geom_bar(stat = "count", position = "dodge", fill="#99CC99") + theme_minimal()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```


```{r echo=FALSE, warning=FALSE, message=FALSE, results=FALSE}
#year

png("./images/fews_year.png", res=300, width = 1500, height = 1500 )
ggplot(crcdata_remove2011, aes(x=year)) + 
    geom_bar(stat="count")+theme_bw() + scale_x_continuous(breaks = crcdata$year) +
  geom_bar(stat = "count", position = "dodge", fill="#99CC99") + theme_minimal() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
dev.off()


```


\newpage




## Level of stakeholder engagement by year - Ghodsvali scale

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(ghodsvali = sprintf("%d_%d_%d_%d", STE_G_nominal, STE_G_instrumental, STE_G_representation, STE_G_transformative))

crcdata_new <- crcdata_new[!(crcdata_new$ghodsvali %in% "0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(ghodsvali = recode(ghodsvali, '0_0_0_0' = 'none', '1_0_0_0' = 'nominal', '0_1_0_0' =  'instrumental', '0_0_1_0' = 'representative',  '0_0_0_1' = 'transformative' ))

crcdata_new$ghodsvali <- as.factor(crcdata_new$ghodsvali)


crcdata_new$ghodsvali <- factor(crcdata_new$ghodsvali, levels = c("nominal", "instrumental", "representative", "transformative"))

my_colors <- c("#99CC99", "#669999", "#6666CC", "#CC9966")

ggplot(crcdata_new, aes(fill=ghodsvali, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year) + scale_fill_manual(values = my_colors, name = "Ghodsvali Scale")


```


```{r echo=FALSE, warning=FALSE, message=FALSE, results=FALSE}

png("./images/fews_ghodsvali.png", res=300, width = 1500, height = 1500 )
ggplot(crcdata_new, aes(fill=ghodsvali, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year) + scale_fill_manual(values = my_colors, name = "Ghodsvali Scale")
dev.off()

```

\newpage

## Level of stakeholder engagement by year - IAP2 scale

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(IAP2 = sprintf("%d_%d_%d_%d_%d_%d", STE_IAP2_data_gathering,STE_IAP2_inform,STE_IAP2_consult,STE_IAP2_involve,STE_IAP2_collab,STE_IAP2_empower))

crcdata_new <- crcdata_new[!(crcdata_new$IAP2 %in% "0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(IAP2 = recode(IAP2, '1_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0' = 'inform', '0_0_1_0_0_0' =  'consult', '0_0_0_1_0_0' = 'involve',  '0_0_0_0_1_0' = 'collab', '0_0_0_0_0_1' =  'empower'))


crcdata_new$IAP2 <- as.factor(crcdata_new$IAP2)


crcdata_new$IAP2 <- factor(crcdata_new$IAP2, levels = c("data gathering", "inform", "consult", "involve", "collab", "empower"))

my_colors <- c("#99CC99", "#669999", "#6666CC", "#9966CC", "#CC9966", "#FFCC66")

ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year) + scale_fill_manual(values = my_colors, name = "IAP2 Scale")


```

```{r echo=FALSE, warning=FALSE, message=FALSE, results=FALSE}

png("./images/fews_iap2.png", res=300, width = 1500, height = 1500 )
ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year) + scale_fill_manual(values = my_colors, name = "IAP2 Scale")

```

\newpage

## Level of stakeholder engagement by year - Local scale

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(local = sprintf("%d_%d_%d_%d_%d_%d_%d_%d", SC_researcher,SC_datagathering,SC_inform,SC_perspectives,SC_plan,SC_identify,SC_envision,SC_implement))


crcdata_new <- crcdata_new[!(crcdata_new$local %in% "0_0_0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(local = dplyr::recode(local, '1_0_0_0_0_0_0_0' ='researcher', '0_1_0_0_0_0_0_0'='data gathering', '0_0_1_0_0_0_0_0' = 'inform', '0_0_0_1_0_0_0_0' =  'perspectives', '0_0_0_0_1_0_0_0' = 'plan',  '0_0_0_0_0_1_0_0' = 'identify', '0_0_0_0_0_0_1_0' =  'envision',  '0_0_0_0_0_0_0_1' = 'implement',  '1_0_0_0_0_0_0_1' ='researcher', '1_1_0_0_0_0_0_0' ='researcher' ))

crcdata_new$local <- as.factor(crcdata_new$local)


crcdata_new$local <- factor(crcdata_new$local, levels = c("researcher", "data gathering", "inform", "perspectives", "plan", "identify", "envision", "implement"))


my_colors <- c("#66FF33", "#339900", "#99CC99", "#669999", "#6666CC", "#9966CC", "#CC9966", "#FFCC66")

ggplot(crcdata_new, aes(fill=local, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year) + scale_fill_manual(values = my_colors, name = "Local Scale")




```
\newpage

## Stakeholder engagement by year

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)
crcdata_st <- read.csv("./data/crc_data_ES2.csv")



my_colors <- c("#99CC99",  "#CC9966")

crcdata_stremove2011 <- subset(crcdata_st, year != "2011")
colnames(crcdata_stremove2011)[22] <- "Stakeholder Engagement"
ggplot(crcdata_stremove2011, aes(fill=`Stakeholder Engagement`, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_st$year) + guides(col=guide_legend("Stakeholder Engagement? Yes or No")) + scale_fill_manual(values = my_colors)



```

\newpage

<!-- ## Level of Stakeholder Engagement by Year - Local -->

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year

# library(dplyr)
# 
# crcdata_new <- crcdata %>% 
#   mutate(IAP2 = sprintf("%d_%d_%d_%d_%d_%d", STE_IAP2_data_gathering,STE_IAP2_inform,STE_IAP2_consult,STE_IAP2_involve,STE_IAP2_collab,STE_IAP2_empower))
# 
# crcdata_new <- crcdata_new[!(crcdata_new$IAP2 %in% "0_0_0_0_0_0"),]
# 
# library(dplyr)
# crcdata_new <- crcdata_new %>%
#     mutate(IAP2 = recode(IAP2, '1_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0' = 'inform', '0_0_1_0_0_0' =  'consult', '0_0_0_1_0_0' = 'involve',  '0_0_0_0_1_0' = 'collab', '0_0_0_0_0_1' =  'empower'))
# 
# ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
#     geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

## Researcher types

```{r echo=FALSE, warning=FALSE, message=FALSE}
#researcher
df <- t(t(colSums(crcdata[,12:17])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(6,4,4,4))
#barplot(df, las=2, main = "Researcher Types")

df <- data.frame(df)
rownames(df) <- c("Engineering", "Physics", "Imterdisciplinary", "Computer Science", "Math", "NGO")
df$group <- row.names(df)
df$group <- factor(df$group, levels=c("Engineering", "Physics", "Imterdisciplinary", "Computer Science", "Math", "NGO"))

ggplot(df, aes(x=group, y=df)) +
    geom_bar(stat='identity', fill="#99CC99")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + guides(col=guide_legend("Researcher Types")) +labs(y= "Count", x = "Researcher Type")


```
\newpage

## Stakeholder types

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder types
df <- t(t(colSums(crcdata[,23:32])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(11,4,4,4))
#barplot(df, las=2, main = "Stakeholder Types")


df <- data.frame(df)
rownames(df) <- c("Combined Government", "Combined Industry", "Farmers", "University", "Combined Coalition", "Public", "Experts", "Tribal Nations", "Youth", "Migrants")
df$group <- row.names(df)
df$group <- factor(df$group, levels=c("Combined Government", "Combined Industry", "Farmers", "University", "Combined Coalition", "Public", "Experts", "Tribal Nations", "Youth", "Migrants"))

ggplot(df, aes(x=group, y=df)) +
    geom_bar(stat='identity', fill="#99CC99")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + guides(col=guide_legend("Stakeholder Types")) +labs(y= "Count", x = "Stakeholder Type")

```
\newpage

## Ghodsvali scale breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#ghodsvali scale
df <- t(t(colSums(crcdata[,33:36])))
df <- df[order(df[,1]),]
par(mar = c(11,4,4,4))

#barplot(c(df[3], df[4], df[2], df[1]), las=2, main="Ghodsvali Scale Breakdown")

df <- data.frame(df)
rownames(df) <- c("Transformative", "Representation", "Nominal", "Instrumental")
df$group <- row.names(df)
library(dplyr)

# create a vector with letters in the desired order
x <- c("Nominal", "Instrumental",        "Representation",   "Transformative" )

df <- df %>%
  slice(match(x, group))



#rownames(df) <- c("Transformative", "Representation", "Nominal", "Instrumental")
#df$group <- row.names(df)
#df <- c(df[3,], df[4,], df[2,], df[1,])
df$group <- factor(df$group, levels=c("Nominal", "Instrumental", "Representation", "Transformative"))

ggplot(df, aes(x=group, y=df)) +
    geom_bar(stat='identity', fill="#99CC99")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + guides(col=guide_legend("Ghodsvali Scale Breakdown")) +labs(y= "Count", x = "Ghodsvali Scale")

```
\newpage

## IAP2 scale breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#IAP2 scale
df <- t(t(colSums(crcdata[,37:42])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(12,4,4,4))
#barplot(c(df[2], df[6], df[1], df[3], df[4], df[5]), las=2, main = "IAP2 Scale Breakdown")


df <- data.frame(df)
rownames(df) <- c("Consulting", "Data Gathering", "Involve", "Collaborative", "Empowered", "Informed")
df$group <- row.names(df)
library(dplyr)

# create a vector with letters in the desired order
x <- c("Data Gathering", "Informed",        "Consulting",   "Involve", "Collaborative", "Empowered" )

df <- df %>%
  slice(match(x, group))



#rownames(df) <- c("Transformative", "Representation", "Nominal", "Instrumental")
#df$group <- row.names(df)
#df <- c(df[3,], df[4,], df[2,], df[1,])
df$group <- factor(df$group, levels=c("Data Gathering", "Informed",        "Consulting",   "Involve", "Collaborative", "Empowered"))

ggplot(df, aes(x=group, y=df)) +
    geom_bar(stat='identity', fill="#99CC99")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + guides(col=guide_legend("Ghodsvali Scale Breakdown")) +labs(y= "Count", x = "IAP2 Scale")




```
\newpage

## Local scale breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#local scale
df <- t(t(colSums(crcdata[,43:50])))
#df <- df[order(df[,1], decreasing = TRUE),]
#par(mar = c(9,4,4,4))
#barplot(df, las=2, main="Local Scale Breakdown")


#barplot(c(df[1], df[3], df[6], df[8], df[4], df[2], df[5], df[7]), las=2, main="Local Scale")





df <- data.frame(df)
rownames(df) <- c("Researcher", "Data Gathering", "Inform", "Perspectives", "Plan", "Identify", "Envision", "Implement")
df$group <- row.names(df)
library(dplyr)

# create a vector with letters in the desired order
#x <- c("Researcher", "Data Gathering",        "Inform",   "Envision", "Collaborative", "Empowered" )

#df <- df %>%
#  slice(match(x, group))



#rownames(df) <- c("Transformative", "Representation", "Nominal", "Instrumental")
#df$group <- row.names(df)
#df <- c(df[3,], df[4,], df[2,], df[1,])
df$group <- factor(df$group, levels=c("Researcher", "Data Gathering", "Inform", "Perspectives", "Plan", "Identify", "Envision", "Implement"))

ggplot(df, aes(x=group, y=df)) +
    geom_bar(stat='identity', fill="#99CC99")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + guides(col=guide_legend("Local Scale Breakdown")) +labs(y= "Count", x = "Local Scale")



```
\newpage

## Geographic location breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geography
df <- t(t(colSums(crcdata[,52:57])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(8,4,4,4))
#barplot(df, las=2, main="Geographic Location Breakdown")




df <- data.frame(df)
rownames(df) <- c("Regional", "Local", "National", "No Geography", "Multinational", "Global")
df$group <- row.names(df)
library(dplyr)

# create a vector with letters in the desired order
#x <- c("Researcher", "Data Gathering",        "Inform",   "Envision", "Collaborative", "Empowered" )

#df <- df %>%
#  slice(match(x, group))



#rownames(df) <- c("Transformative", "Representation", "Nominal", "Instrumental")
#df$group <- row.names(df)
#df <- c(df[3,], df[4,], df[2,], df[1,])
df$group <- factor(df$group, levels=c("Regional", "Local", "National", "No Geography", "Multinational", "Global"))

ggplot(df, aes(x=group, y=df)) +
    geom_bar(stat='identity', fill="#99CC99")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + guides(col=guide_legend("Geography")) +labs(y= "Count", x = "Geography")

```


```{r echo=FALSE, warning=FALSE, message=FALSE}

#Odds of stakeholder scale predicting whether a solution was proposed or not

#set.seed(101) 
#sample = sample.split(crcdata, SplitRatio = .75)
#train = subset(crcdata, sample == TRUE)
#test  = subset(crcdata, sample == FALSE)


ghodsvali.fit<-glm(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,binomial(link = "logit"), data = crcdata)
IAP2.fit<-glm(solution_proposed_YN ~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower,binomial(link = "logit"), data = crcdata)
local.fit<-glm(solution_proposed_YN ~SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement,binomial(link = "logit"), data = crcdata)

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
#--sequentially compares the smaller model with the next more 
#--complex model by adding one variable in each step. Each of those 
#--comparisons is done via a likelihood ratio test 

#anova_ghodsvali_logit <- anova(ghodsvali.fit, test="Chisq")
#anova_IAP2_logit <- anova(IAP2.fit, test="Chisq")
#anova_local_logit <- anova(local.fit, test="Chisq")

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

#prediction_accuracy <- predict(ghodsvali.fit, test, type="response", interval="confidence")
```

\newpage
# Ghodsvali Scale Modeling - solution proposed

## Ghodsvali scale regression

Ghodsvali scale regression testing on whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(ghodsvali.fit)

```
\newpage

## Ghodsvali scale odds

Odds of Ghodsvali scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

logistic.display(ghodsvali.fit)


```

\newpage

## Ghodsvali Ensembled Decision Tree with Feature Importance 

Ghodsvali ensembled decision tree with solution proposed being the dependent variable

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
library(pROC)
library(ROCR)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
# p2 <- predict(rf, test, type="prob")
# p2a <- predict(rf, test)
# p2_df <- as.data.frame(p2)
# p2a_df <- as.data.frame(p2a)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)


#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

ind_rev <- sample(2, nrow(solution_proposed_YN_combo), replace = TRUE, prob = c(0.7, 0.3))
train_rev <- solution_proposed_YN_combo[ind_rev==1,]
test_rev <- solution_proposed_YN_combo[ind_rev==2,]

rf2 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, test_rev)
confusionMatrix(p2_nosolution, test_rev$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Mode - Top 10 - Variable Importance")
importance(rf2)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


# roc_pred <- prediction(p2_df[2], p2a_df)
# perf <- performance(roc_pred, "tpr", "fpr")
# plot(perf)
```


\newpage

# IAP2 Scale Modeling - solution proposed

## IAP2 scale regression 

IAP2 scale regression testing on whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(IAP2.fit)

```

\newpage

## IAP2 scale odds

Odds of IAP2 scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

logistic.display(IAP2.fit)

```
\newpage

## IAP2 Ensembled Decision Tree with Feature Importance 

IAP2 ensembled decision tree with solution proposed being the dependent variable

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)


#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

rf2 <- randomForest(solution_proposed_YN ~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, crcdata_nosolution)
#confusionMatrix(p2_nosolution, test$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Mode - Top 10 - Variable Importance")
importance(rf2)


#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


```


\newpage

# Local Scale Modeling - solution proposed 

## Local scale regression

Local scale regression predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(local.fit)

```

\newpage

## Local scale odds

Odds of Local scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

logistic.display(local.fit)

```

## Local scale Ensembled Decision Tree with Feature Importance 

Local scale ensembled decision tree with solution proposed being the dependent variable

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)

#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

rf2 <- randomForest(solution_proposed_YN ~SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, crcdata_nosolution)
#confusionMatrix(p2_nosolution, test$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Mode - Top 10 - Variable Importance")
importance(rf2)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()



```

\newpage

# Stakeholder Engagement Modeling - solution proposed

## QUESTION: Does engaging stakeholders increase the likelihood that a solution will be proposed/implemented?

Here we use classical logistic regression using a binomial function to determine if engaging stakeholders (Y/N) increases the odds that a solution will be proposed.


```{r echo=FALSE, warning=FALSE, message=FALSE}

#engagement of stakeholders vs. solutions

stakeholder_vs_solutions <-glm(solution_proposed_YN ~S_stakeholder_engagment_YN,family=binomial,data=crcdata)

summary(stakeholder_vs_solutions)
#logistic.display(stakeholder_vs_solutions)

```


\newpage

## ODDS RATIOS: Does engaging stakeholders increase the likelihood that a solution will be proposed/implemented?

Odds of whether engaging stakeholders increases the likelihood that a solution will be proposed?

```{r echo=FALSE, warning=FALSE, message=FALSE}

#engagement of stakeholders vs. solutions

stakeholder_vs_solutions <-glm(solution_proposed_YN ~S_stakeholder_engagment_YN,family=binomial,data=crcdata)

#summary(stakeholder_vs_solutions)
logistic.display(stakeholder_vs_solutions)

```


\newpage

# Compuational Model used Modeling - solution proposed

## QUESTION: Does the use of a computational model increase the likelihood that a solution will be proposed?

Here we use classical logistic regression using a binomial function to determine if the use of a computational model (Y/N) increases the odds that a solution will be proposed.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of computational model vs. solutions

model_vs_solutions <-glm(solution_proposed_YN ~S_model_YN,family=binomial,data=crcdata)

summary(model_vs_solutions)
#logistic.display(model_vs_solutions)

```


\newpage

## ODDS RATIOS: Does the use of a computational model increase the likelihood that a solution will be proposed?

Odds of whether the use of a computational model increases the likelihood that a solution will be proposed.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of computational model vs. solutions

solutions_vs_model <-glm(solution_proposed_YN ~ S_model_YN,family=binomial,data=crcdata)

#summary(model_vs_solutions)
logistic.display(solutions_vs_model)

```


\newpage

# Computational model AND Stakeholder Engagement - solution proposed

## QUESTION: Does the use of a computational model PLUS stakeholder engagement increase the likelihood that a solution is proposed/implemented?

Regression testing for Ghodsvali scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of a computational model AND stakeholder engagement - solution proposed

model_engagement_solution <-glm(solution_proposed_YN ~ S_model_YN * S_stakeholder_engagment_YN,family=binomial,data=crcdata)

summary(model_engagement_solution)

```

\newpage

## ODDS RATIOS: Does the use of a computational model PLUS stakeholder engagement increase the likelihood that a solution is proposed/implemented?

Odds ratios of whether the use of a computational model PLUS stakeholder engagement increase the likelihood that a solution is proposed/implemented?

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of a computational model AND stakeholder engagement - solution proposed

logistic.display(model_engagement_solution)

```

\newpage

# Ghodsvali Modeling - Computational Model

## QUESTION: As the level of Ghodsvali stakeholder engagement increases, does the likelihood of using a computational model increase?

Regression testing for Ghodsvali scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of computational model vs. solutions

ghodsvali_vs_model <-glm(S_model_YN ~ STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,family=binomial,data=crcdata)
local_vs_model <-glm(S_model_YN ~ SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement,family=binomial,data=crcdata)
IAP2_vs_model <-glm(S_model_YN ~ STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower,family=binomial,data=crcdata)

#summary(model_vs_solutions)
#logistic.display(scales_vs_model)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(ghodsvali_vs_model)

```

\newpage

## ODDS RATIOS: As the level of Ghodsvali stakeholder engagement increases, does the odds of using a computational model increase?

Odds ratio for Ghodsvali scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

logistic.display(ghodsvali_vs_model)

```


\newpage

## DECISION TREE: Ghodsvali Ensembled Decision Tree vs whether a computational model was used

Ensembled decision tree for Ghodsvali scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(S_model_YN ~ STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)

#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

rf2 <- randomForest(S_model_YN ~ STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, crcdata_nosolution)
#confusionMatrix(p2_nosolution, test$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Mode - Top 10 - Variable Importance")
importance(rf2)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


```

\newpage

# IAP2 Modeling - Computational Model

## QUESTION: As the level of IAP2 stakeholder engagement increases, does the likelihood of using a computational model increase?

Regression testing for IAP2 scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(IAP2_vs_model)

```

\newpage

## ODDS RATIOS: As the level of Ghodsvali stakeholder engagement increases, does the odds of using a computational model increase?

Odds ratio for IAP2 scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

logistic.display(IAP2_vs_model)

```
\newpage

## DECISION TREE: IAP2 Ensembled Decision Tree vs whether a computational model was used

Ensembled decision tree for IAP2 scale used to predict if a computational model was used (Y/N)


```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(S_model_YN ~ STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)

#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

rf2 <- randomForest(S_model_YN ~ STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, crcdata_nosolution)
#confusionMatrix(p2_nosolution, test$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Mode - Top 10 - Variable Importance")
importance(rf2)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


```

\newpage

# Local Modeling - Computational Model

## QUESTION: As the level of Local scale stakeholder engagement increases, does the likelihood of using a computational model increase?

Regression testing for Local scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(local_vs_model)

```

\newpage

## ODDS RATIOS: As the level of Ghodsvali stakeholder engagement increases, does the odds of using a computational model increase?

Odds ratio for Local scale used to predict if a computational model was used (Y/N)

```{r echo=FALSE, warning=FALSE, message=FALSE}

logistic.display(local_vs_model)

```

\newpage

## DECISION TREE: Local scale Ensembled Decision Tree vs whether a computational model was used

Ensembled decision tree for Local scale used to predict if a computational model was used (Y/N)


```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(S_model_YN ~ SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)

#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

rf2 <- randomForest(S_model_YN ~ STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, crcdata_nosolution)
#confusionMatrix(p2_nosolution, test$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Mode - Top 10 - Variable Importance")
importance(rf2)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


```


\newpage

## Diversity of stakeholders vs solution

## QUESTION: Does the diversity of stakeholders increase the likelihood that a solution will be proposed?

Regression testing of whether Diversity of stakeholders predicts if a solution was proposed (Y/N).  In order to represent diversity, we have used a simple ratio calcuation which sums the number of stakeholders involved divided by the total number of possible stakeholder options.  A ratio which is closer to 1 has a greater level of stakeholder diversity.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of stakeholders vs solutions (using ratio)

crcdata$ST_ratio <- rowSums(crcdata[,23:31])/9

stratio_vs_solutions <-glm(solution_proposed_YN ~ ST_ratio,family=binomial,data=crcdata)

summary(stratio_vs_solutions)
#logistic.display(stratio_vs_solutions)

```

\newpage

## ODDS RATIOS: Does the diversity of stakeholders increase the likelihood that a solution will be proposed?

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of stakeholders vs solutions (using ratio)

logistic.display(stratio_vs_solutions)

```

## QUESTION: If diversity of stakeholders does not increase proposing/implementing solutions, which stakeholders are more associated with proposing/implementing solutions?

Regression testing for diversity of stakeholders used to predict whether a solution was proposed

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of stakeholders vs solutions (using ratio)

stratio_vs_solutions <-glm(solution_proposed_YN ~ ST_farmers + ST_combined_gov  + ST_combined_coalition + ST_combined_industry + ST_public + ST_university + ST_experts,family=binomial,data=crcdata)

summary(stratio_vs_solutions)

#logistic.display(stratio_vs_solutions)

```


## ODDS RATIOS: Diversity of stakeholders vs solution

Odds whether Diversity of stakeholders predicts if a solution was proposed (Y/N). In order to represent diversity, we have used a simple ratio calculation which sums the number of stakeholders involved divided by the total number of possible stakeholder options.  A ratio which is closer to 1 has a greater level of stakeholder diversity.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of stakeholders vs solutions (using ratio)

stratio_vs_solutions <-glm(solution_proposed_YN ~ ST_farmers + ST_combined_gov  + ST_combined_coalition + ST_combined_industry  + ST_public + ST_university + ST_experts,family=binomial,data=crcdata)

#summary(stratio_vs_solutions)
logistic.display(stratio_vs_solutions)

```

## DECISION TREE: Ensembed Decision Tree - Diversity of stakeholders vs solution -->


```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~ST_farmers + ST_combined_gov  + ST_combined_coalition + ST_combined_industry + ST_migrants + ST_public + ST_university + ST_experts, data=train, proximity=TRUE, importance=TRUE)
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()



```



\newpage

# Researcher Diversity Modeling - solution proposed

## QUESTION: Does the diversity of researchers increases the likelihood that a solution will be proposed?

Regression of whether Diversity of researchers predicts if a solution was proposed (Y/N). In order to represent diversity, we have used a simple ratio calculation which sums the number of researcher types involved, divided by the total number of possible researcher options.  A ratio which is closer to 1 has a greater level of researcher diversity.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of researchers vs solutions (using ratio)


crcdata$R_ratio <- rowSums(crcdata[,12:21])/10

rratio_vs_solutions <-glm(solution_proposed_YN ~ R_ratio,family=binomial,data=crcdata)

summary(rratio_vs_solutions)
#logistic.display(rratio_vs_solutions)

```


\newpage

## ODDS RATIOS: Does the diversity of researchers increases the likelihood that a solution will be proposed?

Odds of whether Diversity of researchers predicts if a solution was proposed (Y/N). In order to represent diversity, we have used a simple ratio calculation which sums the number of researcher types involved, divided by the total number of possible researcher options.  A ratio which is closer to 1 has a greater level of researcher diversity.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of researchers vs solutions (using ratio)


crcdata$R_ratio <- rowSums(crcdata[,12:21])/10

rratio_vs_solutions <-glm(solution_proposed_YN ~ R_ratio,family=binomial,data=crcdata)

#summary(rratio_vs_solutions)
logistic.display(rratio_vs_solutions)

```


<!-- ## Interdisciplinary Researchers vs Solution - Regression Testing -->

<!-- In order to accurately reflect diversity of researchers, we run a binomial logistic regression of the interdisciplinary researchers category to assess predictability on stakeholder solution (Y/N). -->

<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->

<!-- #Diversity of researchers vs solutions (using ratio) -->


<!-- crcdata$R_ratio <- rowSums(crcdata[,12:21])/10 -->

<!-- rratio_vs_solutions <-glm(solution_proposed_YN ~ R_interdis,family=binomial,data=crcdata) -->

<!-- summary(rratio_vs_solutions) -->
<!-- #logistic.display(rratio_vs_solutions) -->

<!-- ``` -->

\newpage

# Stakeholder Engagement Modeling - Ghodsvali

## Regression Testing - Stakeholder type vs level of engagement (Ghodsvali)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement ghodsvali

ST_engagement<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,data=crcdata)

summary(ST_engagement)


```
<!-- \newpage -->
<!-- ## Stakeholder type vs level of engagement (Ghodsvali) -->
<!-- ) -->
<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->

<!-- #stakeholder type vs level of engagement ghodsvali -->

<!-- ST_engagement_ghodsvali<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,data=crcdata) -->


<!-- ``` -->

\newpage

# Stakeholder Engagement Modeling - IAP2

## Regression Testing - Stakeholder type vs level of engagement (IAP2)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement IAP2

ST_engagement_IAP2<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower,data=crcdata)

summary(ST_engagement_IAP2)

```

\newpage

# Stakeholder Engagement Modeling - Local

## Regression Testing - Stakeholder type vs level of engagement (local) 

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement local

ST_engagement_local<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement,data=crcdata)

summary(ST_engagement_local)


```

\newpage

## Regression Testing - Stakeholder type vs solution 

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs solution

ST_solution <- glm(solution_proposed_YN~ST_farmers+ST_combined_gov+ST_tribal+ST_combined_coalition+ST_combined_industry+ST_migrants+ST_youth+ST_public+ST_university+ST_experts, family=binomial, data=crcdata)

summary(ST_solution)

```

\newpage

# Geographic Location Modeling - solution proposed

## QUESTION: Does the geographic location of the study increase the likelihood of proposed/implemented solutions?

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_solution <- glm(solution_proposed_YN~G_notdescribed+G_local+G_regional+G_national+G_multination+G_global, family=binomial, data=crcdata)
summary(geog_solution)
#logistic.display(geog_solution)


```

\newpage

## ODDS RATIOS: Does the geographic location of the study increase the likelihood of proposed/implemented solutions?

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

logistic.display(geog_solution)


```

\newpage

## DECISON TREE: Geographic area Ensembed Decision Tree - Geographic area vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~G_notdescribed+G_local+G_regional+G_national+G_multination+G_global, data=train, proximity=TRUE, importance=TRUE) 
print(rf)

p2 <- predict(rf, test)
confusionMatrix(p2, test$solution_proposed_YN)

hist(treesize(rf),
     main = "No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Top 10 - Variable Importance")
importance(rf)

#----new model on data where there is no solution proposed

crcdata_solution <- subset(crcdata, solution_proposed_YN == "Y")
crcdata_nosolution <- subset(crcdata, solution_proposed_YN == "N")
crcdata_stakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "Y")
crcdata_nostakeholders <- subset(crcdata, S_stakeholder_engagment_YN == "N")
sample_crcdata_nosolution <- sample_n(crcdata_nosolution, 30)

solution_proposed_YN_combo <- rbind(crcdata_solution, sample_crcdata_nosolution)

rf2 <- randomForest(solution_proposed_YN ~G_notdescribed+G_local+G_regional+G_national+G_multination+G_global, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

# rf3 <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=solution_proposed_YN_combo, proximity=TRUE, importance=TRUE) 

p2_nosolution <- predict(rf2, crcdata_nosolution)
#confusionMatrix(p2_nosolution, test$solution_proposed_YN)


hist(treesize(rf2),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf2,
           main = "Balanced Model - Top 10 - Variable Importance")
importance(rf2)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


```

\newpage

# Multivariate Stakeholder Engagement Modeling - geographic area

## Regression Testing - stakeholder type vs geographic area - interactions and effects

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_stakeholdertype <- lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~G_notdescribed+G_local+G_regional+G_national+G_multination+G_global, data=crcdata)

summary(geog_stakeholdertype)

```

\newpage

# Multivariate Geographic Modeling - Ghodsvali

## Regression Testing - Geographic area vs engagment (Ghodsvali) - interactions and effects

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_engagment_ghodsvali <- lm(cbind(G_notdescribed,G_local,G_regional,G_national,G_multination,G_global)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=crcdata)

summary(geog_engagment_ghodsvali)

```
\newpage

# Multivariate Geographic Modeling - IAP2

## Regression Testing - Geographic area vs engagment (IAP2) - interactions and effects
```{r echo=FALSE, warning=FALSE, message=FALSE}


geog_engagment_IAP2 <- lm(cbind(G_notdescribed,G_local,G_regional,G_national,G_multination,G_global)~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower, data=crcdata)

summary(geog_engagment_IAP2)

```
\newpage

# Multivariate Geographic Modeling - Local

## Regression Testing - Geographic area vs engagment (local) - interactions and effects
```{r echo=FALSE, warning=FALSE, message=FALSE}


geog_engagment_local <- lm(cbind(G_notdescribed,G_local,G_regional,G_national,G_multination,G_global)~SC_researcher+SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement, data=crcdata)

summary(geog_engagment_local)

```

\newpage

# ADDITIONAL ANALYSIS -  ALL VARIABLES 

## Looking at Decision Tree for all variables - with Ghodsvali scale - with solution proposed as dependent variable

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative+ST_combined_gov+           ST_tribal+ST_combined_coalition+ST_combined_industry+ST_migrants+ST_youth+ST_public+ST_university+ST_experts+G_local+G_regional+G_national+G_multination+G_global+G_nogeography+year, data=train, proximity=TRUE, importance=TRUE) 
print(rf)


#----new model on data where there is no solution proposed

hist(treesize(rf),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Balanced Model - Top 10 - Variable Importance")
importance(rf)

#--

# Required libraries
library(randomForest)
library(ggplot2)


# Extract variable importance
var_imp <- importance(rf2, type = 2)  # type = 2 is MeanDecreaseGini
var_imp_df <- data.frame(Variable = rownames(var_imp),
                         MeanDecreaseGini = var_imp[, "MeanDecreaseGini"])

# Sort and select top 10
var_imp_df <- var_imp_df[order(-var_imp_df$MeanDecreaseGini), ]
top_vars <- head(var_imp_df, 10)

# Plot
ggplot(top_vars, aes(x = reorder(Variable, MeanDecreaseGini), y = MeanDecreaseGini)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 10 Variable Importance - Random Forest Model",
       x = "Variable", y = "Mean Decrease in Gini") +
  theme_minimal()


```

\newpage

# ADDITIONAL ANALYSIS -  ALL VARIABLES - minus scaling

## Looking at Decision Tree for all variables - minus the Ghodsvali scale - with solution proposed as dependent variable

```{r echo=FALSE, warning=FALSE, message=FALSE}

#RF scales

library(randomForest)
library(caret)
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind==1,]
test <- crcdata[ind==2,]
rf <- randomForest(solution_proposed_YN ~ST_combined_gov+           ST_tribal+ST_combined_coalition+ST_combined_industry+ST_migrants+ST_youth+ST_public+ST_university+ST_experts+G_local+G_regional+G_national+G_multination+G_global+G_nogeography+year, data=train, proximity=TRUE, importance=TRUE) 
print(rf)


#----new model on data where there is no solution proposed

hist(treesize(rf),
     main = "Balanced Model - No. of Nodes for the Trees",
     col = "green")
varImpPlot(rf,
           main = "Balanced Model - Top 10 - Variable Importance")
importance(rf)


```
\newpage

## Representative Decision Tree Plot - Balanced Model - Minus Scaling

```{r echo=FALSE, warning=FALSE, message=FALSE}


library(rpart)
library(rpart.plot)

# Make sure your response is a factor for classification
train$solution_proposed_YN <- as.factor(train$solution_proposed_YN)

# Fit a decision tree using rpart
tree_model <- rpart(
  solution_proposed_YN ~ ST_combined_gov + ST_tribal + ST_combined_coalition +
    ST_combined_industry + ST_migrants + ST_youth + ST_public + ST_university +
    ST_experts + G_local + G_regional + G_national + G_multination +
    G_global + G_nogeography + year,
  data = train,
  method = "class",  # use "anova" for regression
  control = rpart.control(cp = 0, minsplit = 2, maxdepth = 5)
)

# Plot the tree
rpart.plot(tree_model)

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(randomForest)
library(reprtree)
library(rpart)
library(rpart.plot)
# Generate representative tree from random forest
rep_tree <- reprtree:::ReprTree(rf, train, metric = "d2")

#reprtree::plot.reprtree(rep_tree$tree)


# Step 2: Plot it using rpart.plot
#rpart.plot::rpart.plot(rep_tree$tree)




```

```{r echo=FALSE, warning=FALSE, message=FALSE}

# Load necessary packages
library(randomForest)
library(reprtree)
library(rpart.plot)

# Ensure your outcome is a factor (classification)
crcdata$solution_proposed_YN <- as.factor(crcdata$solution_proposed_YN)

# Train-test split
set.seed(2223)
ind <- sample(2, nrow(crcdata), replace = TRUE, prob = c(0.7, 0.3))
train <- crcdata[ind == 1, ]
test <- crcdata[ind == 2, ]

# Fit random forest
rf <- randomForest(
  solution_proposed_YN ~ ST_combined_gov + ST_tribal + ST_combined_coalition +
    ST_combined_industry + ST_migrants + ST_youth + ST_public + ST_university +
    ST_experts + G_local + G_regional + G_national + G_multination +
    G_global + G_nogeography + year,
  data = train,
  proximity = TRUE,
  importance = TRUE
)

# Generate representative tree
rep_tree <- reprtree:::ReprTree(rf, train, metric = "d2")

#single tree

rep_tree2 <- rpart(solution_proposed_YN ~ ST_combined_gov + ST_tribal + ST_combined_coalition +
    ST_combined_industry + ST_migrants + ST_youth + ST_public + ST_university +
    ST_experts + G_local + G_regional + G_national + G_multination +
    G_global + G_nogeography + year,
  data = train)

# plot the tree
#rpart.plot(rpart.plot::as.rpart(rep_tree))

```



