---
title: "CRC Engage"
author: "Erich Seamon"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\newpage

# CRC Engage Summary

CRC Engage Summary Statement

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(ggplot2)
library(epiDisplay)

crcdata <- read.csv("./data/crc_data_ES2.csv")


#set YN to 01
require(dplyr)
crcdata <- crcdata %>%
  mutate(solution_proposed_YN = ifelse(solution_proposed_YN == "N",0,1))

require(dplyr)
crcdata <- crcdata %>%
  mutate(solution_implemented_YN = ifelse(solution_implemented_YN == "N",0,1))

require(dplyr)
crcdata <- crcdata %>%
  mutate(S_stakeholder_engagment_YN = ifelse(S_stakeholder_engagment_YN == "N",0,1))

#fix colnames
names(crcdata)[names(crcdata) == 'STE_IAP2_NA'] <- 'STE_IAP2_data_gathering'
names(crcdata)[names(crcdata) == 'G_na'] <- 'G_nogeography'

```

\newpage

# Chi Square Tests

## Comparing categorical independence

For more info on this topic see:

Kim HY. Statistical notes for clinical researchers: Chi-squared test and Fisher's exact test. Restor Dent Endod. 2017 May;42(2):152-155. doi: 10.5395/rde.2017.42.2.152. Epub 2017 Mar 30. PMID: 28503482; PMCID: PMC5426219.


## Chi Square - Solution vs. Stakeholder Engagement

Chi Square and Fishers Exact Test on contingency table with Solution/No Solution as the explanatory, and engaged stakeholder/did not engage stakeholder as the response.

Both chi square and fishers exact test were significant, with a chi square approximation of ~44, which is well above the critical value (3.84 for one degree of freedom).  Fishers exact test returned an odds ratio of ~18. The alternative hypothesis: true odds ratio is not equal to 1. Null is rejected. The groups are not independent.

The FET defaults to associating the odds ratio (which can represent effect size) with the first cell. In this instance "The odds of having a solution is 18.25 times that for an engaged stakeholder".  You could flip the response and explanatory, but the odds ratio would stay the same.


```{r, echo=FALSE}
library(Barnard)

solution_stakeholder <- 
  as.matrix(
    read.table(text=
                 "  E     NE           
      S             14    4      
      NS            76    400",
               header=TRUE,
               row.names=1)
  )

names(dimnames(solution_stakeholder)) <- c('solution','stakeholder')
solution_stakeholder

solution_stakeholder <- as.table(solution_stakeholder)

summary(solution_stakeholder)

fisher.test(solution_stakeholder)

barnard.test(14,4,76,400)


```

\newpage

## Chi Square - Solution vs. Model 

Chi Square and Fishers Exact Test on contingency table with Solution/No Solution as the explanatory, and Model/No Model as the response.

Both chi square and fishers exact test were insignificant/borderline, with a chi square approximation of ~3.7, which is below to the critical value (3.84 for one degree of freedom).  Fishers exact test returned an odds ratio of under 1. Null is accepted. The groups are independent.

The FET defaults to associating the odds ratio (which can represent effect size) with the first cell. In this instance "The odds of having a solution is .39 times that for having a model".  You could flip the response and explanatory, but the odds ratio would stay the same.

```{r, echo=FALSE}
library(Barnard)

solution_model <- 
  as.matrix(
    read.table(text=
                 "  M     NM      
      S             11    7      
      NS            377   94",
               header=TRUE,
               row.names=1)
  )

names(dimnames(solution_model)) <- c('solution','model')
solution_model

solution_model <- as.table(solution_model)

summary(solution_model)

fisher.test(solution_model)

barnard.test(11,7,377,94)
```

\newpage

# Graphs

## Proposed Solution Papers

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(crcdata,aes(x=solution_proposed_YN, fill=year)) + ggtitle("Solution Proposed: Y=18") +
  geom_bar(stat = "count", position = "dodge", fill="gray", color="black") + theme_minimal()

```
\newpage

## Implemented Solution Papers

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(crcdata,aes(x=solution_implemented_YN, fill=year)) + ggtitle("Solution Implemented: Y=11") +
  geom_bar(stat = "count", position = "dodge", fill="gray", color="black") + theme_minimal()

```
\newpage

## Solution Types
```{r echo=FALSE, warning=FALSE, message=FALSE}

par(mar = c(8,4,4,4))
barplot(colSums(crcdata[,4:10]), las=2, main="Solution Types: N=18")

```
\newpage

## Computational Model Used

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(crcdata,aes(x=S_model_YN, fill=year)) + ggtitle("Computational Model Used: Y=366") +
  geom_bar(stat = "count", position = "dodge", fill="gray", color="black") + theme_minimal()
 
``` 
\newpage

## Stakeholder Engagement

```{r echo=FALSE, warning=FALSE, message=FALSE}

# nrow(subset(crcdata, solution_proposed_YN == "1"))/nrow(subset(crcdata, solution_proposed_YN == "0"))
# 
# nrow(subset(crcdata, solution_implemented_YN == "1"))/nrow(subset(crcdata, solution_implemented_YN == "0"))


#stakeholder
par(mar = c(4,4,4,4))
barplot(table(crcdata$S_stakeholder_engagment_YN), main = "Stakeholder Engagment: N=92")

```
\newpage

## All FEWS Papers by Year

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
ggplot(crcdata, aes(x=year)) + 
    geom_bar(stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata$year)

```
\newpage

## Level of Stakeholder Engagement by Year - Ghodsvali

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(ghodsvali = sprintf("%d_%d_%d_%d", STE_G_nominal, STE_G_instrumental, STE_G_representation, STE_G_transformative))

crcdata_new <- crcdata_new[!(crcdata_new$ghodsvali %in% "0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(ghodsvali = recode(ghodsvali, '0_0_0_0' = 'none', '1_0_0_0' = 'nominal', '0_1_0_0' =  'instrumental', '0_0_1_0' = 'representation',  '0_0_0_1' = 'transformative' ))

ggplot(crcdata_new, aes(fill=ghodsvali, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

## Level of Stakeholder Engagement by Year - IAP2

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(IAP2 = sprintf("%d_%d_%d_%d_%d_%d", STE_IAP2_data_gathering,STE_IAP2_inform,STE_IAP2_consult,STE_IAP2_involve,STE_IAP2_collab,STE_IAP2_empower))

crcdata_new <- crcdata_new[!(crcdata_new$IAP2 %in% "0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(IAP2 = recode(IAP2, '1_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0' = 'inform', '0_0_1_0_0_0' =  'consult', '0_0_0_1_0_0' = 'involve',  '0_0_0_0_1_0' = 'collab', '0_0_0_0_0_1' =  'empower'))

ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```

\newpage

## Level of Stakeholder Engagement by Year - Local

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(local = sprintf("%d_%d_%d_%d_%d_%d_%d_%d", SC_datagathering,SC_inform,SC_perspectives,SC_plan,SC_identify,SC_envision,SC_implement,SC_notdescribed))


crcdata_new <- crcdata_new[!(crcdata_new$local %in% "0_0_0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(local = recode(local, '1_0_0_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0_0_0' = 'inform', '0_0_1_0_0_0_0_0' =  'perspectives', '0_0_0_1_0_0_0_0' = 'plan',  '0_0_0_0_1_0_0_0' = 'identify', '0_0_0_0_0_1_0_0' =  'envision',  '0_0_0_0_0_0_1_0' = 'implement', '0_0_0_0_0_0_0_1' =  'not described'))

ggplot(crcdata_new, aes(fill=local, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

## Stakeholder Engagement by Year

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)
crcdata_st <- read.csv("./data/crc_data_ES2.csv")

ggplot(crcdata_st, aes(fill=S_stakeholder_engagment_YN, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_st$year)


```

\newpage

## Level of Stakeholder Engagement by Year - Local

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(IAP2 = sprintf("%d_%d_%d_%d_%d_%d_%d", STE_IAP2_data_gathering,STE_IAP2_inform,STE_IAP2_consult,STE_IAP2_involve,STE_IAP2_collab,STE_IAP2_empower,STE_IAP2_researcher))

crcdata_new <- crcdata_new[!(crcdata_new$IAP2 %in% "0_0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(IAP2 = recode(IAP2, '1_0_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0_0' = 'inform', '0_0_1_0_0_0_0' =  'consult', '0_0_0_1_0_0_0' = 'involve',  '0_0_0_0_1_0_0' = 'collab', '0_0_0_0_0_1_0' =  'empower', '0_0_0_0_0_0_1' = 'researcher'))

ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

## Researcher Types
```{r echo=FALSE, warning=FALSE, message=FALSE}
#researcher
df <- t(t(colSums(crcdata[,12:17])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(6,4,4,4))
barplot(df, las=2, main = "Researcher Types")

```
\newpage

## Stakeholder Types

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder types
df <- t(t(colSums(crcdata[,23:32])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(11,4,4,4))
barplot(df, las=2, main = "Stakeholder Types")

```
\newpage

## Ghodsvali Scale Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#ghodsvali scale
df <- t(t(colSums(crcdata[,33:36])))
df <- df[order(df[,1], decreasing = TRUE),]
barplot(df, las=2, main="Ghodsvali Scale Breakdown")

```
\newpage

## IAP2 Scale Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#IAP2 scale
df <- t(t(colSums(crcdata[,37:43])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(12,4,4,4))
barplot(df, las=2, main = "IAP2 Scale Breakdown")

```
\newpage

## Local Scale Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#local scale
df <- t(t(colSums(crcdata[,44:51])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(9,4,4,4))
barplot(df, las=2, main="Local Scale Breakdown")

```
\newpage

## Geographic Location Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geography
df <- t(t(colSums(crcdata[,52:57])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(8,4,4,4))
barplot(df, las=2, main="Geographic Location Breakdown")

```


```{r echo=FALSE, warning=FALSE, message=FALSE}

#Odds of stakeholder scale predicting whether a solution was proposed or not

ghodsvali.fit<-glm(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,family=binomial,data=crcdata)
IAP2.fit<-glm(solution_proposed_YN ~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower+STE_IAP2_researcher,family=binomial,data=crcdata)

local.fit<-glm(solution_proposed_YN ~SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement+SC_notdescribed,family=binomial,data=crcdata)

```

\newpage
# Regression Testing

## Ghodsvali

Odds of stakeholder scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(ghodsvali.fit)
logistic.display(ghodsvali.fit)


```

\newpage

## IAP2

Odds of stakeholder scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(IAP2.fit)
logistic.display(IAP2.fit)


```

\newpage

## Local

Odds of stakeholder scale predicting whether a solution was proposed or not
```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(local.fit)
logistic.display(local.fit)


```


\newpage

## Engagement vs. solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#engagement of stakeholders vs. solutions

stakeholder_vs_solutions <-glm(solution_proposed_YN ~S_stakeholder_engagment_YN,family=binomial,data=crcdata)

summary(stakeholder_vs_solutions)
logistic.display(stakeholder_vs_solutions)

```
\newpage

## Use of computational model vs. solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of computational model vs. solutions

model_vs_solutions <-glm(solution_proposed_YN ~S_model_YN,family=binomial,data=crcdata)

summary(model_vs_solutions)
logistic.display(model_vs_solutions)

```
\newpage

## Diversity of stakeholders vs solution


```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of stakeholders vs solutions (using ratio)

crcdata$ST_ratio <- rowSums(crcdata[,23:32])/10

stratio_vs_solutions <-glm(solution_proposed_YN ~ ST_ratio,family=binomial,data=crcdata)

summary(stratio_vs_solutions)
logistic.display(stratio_vs_solutions)

```
\newpage

## Interdisciplinary Researchers vs Solution

In order to accurately reflect diversity of researchers, we run a binomial logistic regression of the interdisciplinary researchers category to assess predictability on stakeholder solution (Y/N).

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of researchers vs solutions (using ratio)


crcdata$R_ratio <- rowSums(crcdata[,12:21])/10

rratio_vs_solutions <-glm(solution_proposed_YN ~ R_interdis,family=binomial,data=crcdata)

summary(rratio_vs_solutions)
logistic.display(rratio_vs_solutions)

```

## Diversity of Researchers vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of researchers vs solutions (using ratio)


crcdata$R_ratio <- rowSums(crcdata[,12:21])/10

rratio_vs_solutions <-glm(solution_proposed_YN ~ R_ratio,family=binomial,data=crcdata)

summary(rratio_vs_solutions)
logistic.display(rratio_vs_solutions)

```
\newpage

## Stakeholder type vs level of engagement (Ghodsvali)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement ghodsvali

ST_engagement<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,data=crcdata)

summary(ST_engagement)


```
<!-- \newpage -->
<!-- ## Stakeholder type vs level of engagement (Ghodsvali) -->
<!-- ) -->
<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->

<!-- #stakeholder type vs level of engagement ghodsvali -->

<!-- ST_engagement_ghodsvali<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,data=crcdata) -->


<!-- ``` -->

\newpage

## Stakeholder type vs level of engagement (IAP2)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement IAP2

ST_engagement_IAP2<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower+STE_IAP2_researcher,data=crcdata)

summary(ST_engagement_IAP2)

```

\newpage

## Stakeholder type vs level of engagement (local)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement local

ST_engagement_IAP2<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement+SC_notdescribed,data=crcdata)

summary(ST_engagement_IAP2)


```

\newpage

## Stakeholder type vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs solution

ST_solution <- glm(solution_proposed_YN~ST_farmers+ST_combined_gov+ST_tribal+ST_combined_coalition+ST_combined_industry+ST_migrants+ST_youth+ST_public+ST_university+ST_experts, family=binomial, data=crcdata)

summary(ST_solution)

```

\newpage

## Geographic area vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_solution <- glm(solution_proposed_YN~G_local+G_regional+G_national+G_multination+G_global, family=binomial, data=crcdata)
summary(geog_solution)
logistic.display(geog_solution)


```

\newpage

## stakeholder type vs geographic area

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_stakeholdertype <- lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~G_local+G_regional+G_national+G_multination+G_global, data=crcdata)

summary(geog_stakeholdertype)

```

\newpage

## Geographic area vs engagment (Ghodsvali)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_engagment_ghodsvali <- lm(cbind(G_local,G_regional,G_national,G_multination,G_global)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=crcdata)

summary(geog_engagment_ghodsvali)

```
\newpage

## Geographic area vs engagment (IAP2)
```{r echo=FALSE, warning=FALSE, message=FALSE}


geog_engagment_IAP2 <- lm(cbind(G_local,G_regional,G_national,G_multination,G_global)~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower+STE_IAP2_researcher, data=crcdata)

summary(geog_engagment_IAP2)

```
\newpage

## Geographic area vs engagment (local)
```{r echo=FALSE, warning=FALSE, message=FALSE}


geog_engagment_local <- lm(cbind(G_local,G_regional,G_national,G_multination,G_global)~SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement+SC_notdescribed, data=crcdata)

summary(geog_engagment_local)

```
