---
title: "CRC Engage"
author: "Erich Seamon"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CRC Engage Summary

CRC Engage Summary Statement

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(ggplot2)
library(epiDisplay)

crcdata <- read.csv("./data/crc_data_ES2.csv")


#set YN to 01
require(dplyr)
crcdata <- crcdata %>%
  mutate(solution_proposed_YN = ifelse(solution_proposed_YN == "N",0,1))

require(dplyr)
crcdata <- crcdata %>%
  mutate(solution_implemented_YN = ifelse(solution_implemented_YN == "N",0,1))

require(dplyr)
crcdata <- crcdata %>%
  mutate(S_stakeholder_engagment_YN = ifelse(S_stakeholder_engagment_YN == "N",0,1))

#fix colnames
names(crcdata)[names(crcdata) == 'STE_IAP2_NA'] <- 'STE_IAP2_data_gathering'
names(crcdata)[names(crcdata) == 'G_na'] <- 'G_nogeography'

```

# Proposed Solution Papers

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(crcdata,aes(x=solution_proposed_YN, fill=year)) + ggtitle("Solution Proposed: Y=18") +
  geom_bar(stat = "count", position = "dodge", fill="gray", color="black") + theme_minimal()

```
\newpage

# Implemented Solution Papers

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(crcdata,aes(x=solution_implemented_YN, fill=year)) + ggtitle("Solution Implemented: Y=11") +
  geom_bar(stat = "count", position = "dodge", fill="gray", color="black") + theme_minimal()

```
\newpage

# Solution Types
```{r echo=FALSE, warning=FALSE, message=FALSE}

par(mar = c(8,4,4,4))
barplot(colSums(crcdata[,4:10]), las=2, main="Solution Types: N=18")

```
\newpage

# Computational Model Used

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(crcdata,aes(x=S_model_YN, fill=year)) + ggtitle("Computational Model Used: Y=366") +
  geom_bar(stat = "count", position = "dodge", fill="gray", color="black") + theme_minimal()
 
``` 
\newpage

# Stakeholder Engagement

```{r echo=FALSE, warning=FALSE, message=FALSE}

# nrow(subset(crcdata, solution_proposed_YN == "1"))/nrow(subset(crcdata, solution_proposed_YN == "0"))
# 
# nrow(subset(crcdata, solution_implemented_YN == "1"))/nrow(subset(crcdata, solution_implemented_YN == "0"))


#stakeholder
par(mar = c(4,4,4,4))
barplot(table(crcdata$S_stakeholder_engagment_YN), main = "Stakeholder Engagment: N=92")

```
\newpage

# All FEWS papers by year

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
ggplot(crcdata, aes(x=year)) + 
    geom_bar(stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata$year)

```
\newpage

# Level of Stakeholder Engagement by Year - Ghodsvali

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(ghodsvali = sprintf("%d_%d_%d_%d", STE_G_nominal, STE_G_instrumental, STE_G_representation, STE_G_transformative))

crcdata_new <- crcdata_new[!(crcdata_new$ghodsvali %in% "0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(ghodsvali = recode(ghodsvali, '0_0_0_0' = 'none', '1_0_0_0' = 'nominal', '0_1_0_0' =  'instrumental', '0_0_1_0' = 'representation',  '0_0_0_1' = 'transformative' ))

ggplot(crcdata_new, aes(fill=ghodsvali, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

# Level of Stakeholder Engagement by Year - IAP2

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(IAP2 = sprintf("%d_%d_%d_%d_%d_%d", STE_IAP2_data_gathering,STE_IAP2_inform,STE_IAP2_consult,STE_IAP2_involve,STE_IAP2_collab,STE_IAP2_empower))

crcdata_new <- crcdata_new[!(crcdata_new$IAP2 %in% "0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(IAP2 = recode(IAP2, '1_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0' = 'inform', '0_0_1_0_0_0' =  'consult', '0_0_0_1_0_0' = 'involve',  '0_0_0_0_1_0' = 'collab', '0_0_0_0_0_1' =  'empower'))

ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```

\newpage

# Level of Stakeholder Engagement by Year - local

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(local = sprintf("%d_%d_%d_%d_%d_%d_%d_%d", SC_datagathering,SC_inform,SC_perspectives,SC_plan,SC_identify,SC_envision,SC_implement,SC_notdescribed))


crcdata_new <- crcdata_new[!(crcdata_new$local %in% "0_0_0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(local = recode(local, '1_0_0_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0_0_0' = 'inform', '0_0_1_0_0_0_0_0' =  'perspectives', '0_0_0_1_0_0_0_0' = 'plan',  '0_0_0_0_1_0_0_0' = 'identify', '0_0_0_0_0_1_0_0' =  'envision',  '0_0_0_0_0_0_1_0' = 'implement', '0_0_0_0_0_0_0_1' =  'not described'))

ggplot(crcdata_new, aes(fill=local, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

# stakeholder engagement by year

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)
crcdata_st <- read.csv("./data/crc_data_ES2.csv")

ggplot(crcdata_st, aes(fill=S_stakeholder_engagment_YN, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_st$year)


```

\newpage

# Level of Stakeholder Engagement by Year - local

```{r echo=FALSE, warning=FALSE, message=FALSE}
#year
library(dplyr)

crcdata_new <- crcdata %>% 
  mutate(IAP2 = sprintf("%d_%d_%d_%d_%d_%d_%d", STE_IAP2_data_gathering,STE_IAP2_inform,STE_IAP2_consult,STE_IAP2_involve,STE_IAP2_collab,STE_IAP2_empower,STE_IAP2_researcher))

crcdata_new <- crcdata_new[!(crcdata_new$IAP2 %in% "0_0_0_0_0_0_0"),]

library(dplyr)
crcdata_new <- crcdata_new %>%
    mutate(IAP2 = recode(IAP2, '1_0_0_0_0_0_0' = 'data gathering', '0_1_0_0_0_0_0' = 'inform', '0_0_1_0_0_0_0' =  'consult', '0_0_0_1_0_0_0' = 'involve',  '0_0_0_0_1_0_0' = 'collab', '0_0_0_0_0_1_0' =  'empower', '0_0_0_0_0_0_1' = 'researcher'))

ggplot(crcdata_new, aes(fill=IAP2, x=year)) + 
    geom_bar(position="stack", stat="count")+theme_bw()+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_x_continuous(breaks = crcdata_new$year)


```
\newpage

# Researcher Types
```{r echo=FALSE, warning=FALSE, message=FALSE}
#researcher
df <- t(t(colSums(crcdata[,12:17])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(6,4,4,4))
barplot(df, las=2, main = "Researcher Types")

```
\newpage

# Stakeholder Types

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder types
df <- t(t(colSums(crcdata[,23:32])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(11,4,4,4))
barplot(df, las=2, main = "Stakeholder Types")

```
\newpage

# Ghodsvali Scale Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#ghodsvali scale
df <- t(t(colSums(crcdata[,33:36])))
df <- df[order(df[,1], decreasing = TRUE),]
barplot(df, las=2, main="Ghodsvali Scale Breakdown")

```
\newpage

# IAP2 Scale Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#IAP2 scale
df <- t(t(colSums(crcdata[,37:43])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(12,4,4,4))
barplot(df, las=2, main = "IAP2 Scale Breakdown")

```
\newpage

# Local Scale Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#local scale
df <- t(t(colSums(crcdata[,44:51])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(9,4,4,4))
barplot(df, las=2, main="Local Scale Breakdown")

```
\newpage

# Geographic Location Breakdown

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geography
df <- t(t(colSums(crcdata[,52:57])))
df <- df[order(df[,1], decreasing = TRUE),]
par(mar = c(8,4,4,4))
barplot(df, las=2, main="Geographic Location Breakdown")

```


```{r echo=FALSE, warning=FALSE, message=FALSE}

#Odds of stakeholder scale predicting whether a solution was proposed or not

ghodsvali.fit<-glm(solution_proposed_YN ~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,family=binomial,data=crcdata)
IAP2.fit<-glm(solution_proposed_YN ~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower+STE_IAP2_researcher,family=binomial,data=crcdata)

local.fit<-glm(solution_proposed_YN ~SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement+SC_notdescribed,family=binomial,data=crcdata)

```

\newpage

# Ghodsvali - Odds of stakeholder scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(ghodsvali.fit)
logistic.display(ghodsvali.fit)


```

\newpage

# IAP2 - Odds of stakeholder scale predicting whether a solution was proposed or not

```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(IAP2.fit)
logistic.display(IAP2.fit)


```

\newpage

# Local - Odds of stakeholder scale predicting whether a solution was proposed or not
```{r echo=FALSE, warning=FALSE, message=FALSE}

summary(local.fit)
logistic.display(local.fit)


```


\newpage

# Engagement vs. solutation

```{r echo=FALSE, warning=FALSE, message=FALSE}

#engagement of stakeholders vs. solutions

stakeholder_vs_solutions <-glm(solution_proposed_YN ~S_stakeholder_engagment_YN,family=binomial,data=crcdata)

summary(stakeholder_vs_solutions)
logistic.display(stakeholder_vs_solutions)

```
\newpage

# Use of computational model vs. solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Use of computational model vs. solutions

model_vs_solutions <-glm(solution_proposed_YN ~S_model_YN,family=binomial,data=crcdata)

summary(model_vs_solutions)
logistic.display(model_vs_solutions)

```
\newpage

# Diversity of stakeholders vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of stakeholders vs solutions (using ratio)

crcdata$ST_ratio <- rowSums(crcdata[,23:32])/10

stratio_vs_solutions <-glm(solution_proposed_YN ~ ST_ratio,family=binomial,data=crcdata)

summary(stratio_vs_solutions)
logistic.display(stratio_vs_solutions)

```
\newpage

# Diversity of Researchers vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#Diversity of researchers vs solutions (using ratio)


crcdata$R_ratio <- rowSums(crcdata[,12:21])/10

rratio_vs_solutions <-glm(solution_proposed_YN ~ R_ratio,family=binomial,data=crcdata)

summary(rratio_vs_solutions)
logistic.display(rratio_vs_solutions)

```
\newpage

# Stakeholder type vs level of engagement (Ghodsvali)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement ghodsvali

ST_engagement<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,data=crcdata)

summary(ST_engagement)


```
<!-- \newpage -->
<!-- ## Stakeholder type vs level of engagement (Ghodsvali) -->
<!-- ) -->
<!-- ```{r echo=FALSE, warning=FALSE, message=FALSE} -->

<!-- #stakeholder type vs level of engagement ghodsvali -->

<!-- ST_engagement_ghodsvali<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative,data=crcdata) -->


<!-- ``` -->

\newpage

# Stakeholder type vs level of engagement (IAP2)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement IAP2

ST_engagement_IAP2<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower+STE_IAP2_researcher,data=crcdata)

summary(ST_engagement_IAP2)

```

\newpage

# Stakeholder type vs level of engagement (local)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs level of engagement local

ST_engagement_IAP2<-lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement+SC_notdescribed,data=crcdata)

summary(ST_engagement_IAP2)


```

\newpage

# Stakeholder type vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#stakeholder type vs solution

ST_solution <- glm(solution_proposed_YN~ST_farmers+ST_combined_gov+ST_tribal+ST_combined_coalition+ST_combined_industry+ST_migrants+ST_youth+ST_public+ST_university+ST_experts, family=binomial, data=crcdata)

summary(ST_solution)

```

\newpage

# Geographic area vs solution

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_solution <- glm(solution_proposed_YN~G_local+G_regional+G_national+G_multination+G_global, family=binomial, data=crcdata)
summary(geog_solution)
logistic.display(geog_solution)


```

\newpage

# stakeholder type vs geographic area

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_stakeholdertype <- lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~G_local+G_regional+G_national+G_multination+G_global, data=crcdata)

summary(geog_stakeholdertype)

```

\newpage

# Geographic area vs engagment (Ghodsvali)

```{r echo=FALSE, warning=FALSE, message=FALSE}

#geographic area vs solution

geog_engagment_ghodsvali <- lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_G_nominal+STE_G_instrumental+STE_G_representation+STE_G_transformative, data=crcdata)

summary(geog_engagment_ghodsvali)

```
\newpage

# Geographic area vs engagment (IAP2)
```{r echo=FALSE, warning=FALSE, message=FALSE}


geog_engagment_IAP2 <- lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~STE_IAP2_data_gathering+STE_IAP2_inform+STE_IAP2_consult+STE_IAP2_involve+STE_IAP2_collab+STE_IAP2_empower+STE_IAP2_researcher, data=crcdata)

summary(geog_engagment_IAP2)

```
\newpage

# Geographic area vs engagment (local)
```{r echo=FALSE, warning=FALSE, message=FALSE}


geog_engagment_local <- lm(cbind(ST_farmers,ST_combined_gov,ST_tribal,ST_combined_coalition,ST_combined_industry,ST_migrants,ST_youth,ST_public,ST_university,ST_experts)~SC_datagathering+SC_inform+SC_perspectives+SC_plan+SC_identify+SC_envision+SC_implement+SC_notdescribed, data=crcdata)

summary(geog_engagment_local)

```
